An ultra-low noise, high-voltage piezo driver

### 2016-01-22 piezo.tex
Added additional info about frontpanel control

@@

>>>>

Control via the frontpanel is provided by a rotary encoder/push button, and a single on/off switch.
The rotary encoder/push button switch allows interaction with a user-definable menu system.
For example, this allows the user to quickly switch the piezo driver into ``ramp'' mode to scan a laser over some resonance feature.

@@

Finally, the high voltage output is interlocked with a signal on the back plane (which can optionally be over-ridden by placing a jumper onboard); this allows easy integration into existing laboratory interlock schemes.
